\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{url}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://www.cs.vt.edu/~jiaoyang/}{\LARGE Yang Jiao}}
	& \href{mailto:jiaoyang@cs.vt.edu}{\url{jiaoyang@vt.edu}}\\
	{\footnotesize \texttt{1979 Milky Way, Verona, WI 53593}} &
	\href{http://www.cs.vt.edu/\%7ejiaoyang/}{\url{http://www.cs.vt.edu/~jiaoyang/}}
	\\
	\end{tabular*}
\\
\vspace{0.1in}}

\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
	\begin{description}
		\item[Programming:] { \footnotesize C, C++, Assembly (x86),
		\LaTeX2e}
		\item[Web:] { \footnotesize PHP5, HTML, JavaScript, VBScript}
		\item[Database:]{ \footnotesize MySQL, MUMPS/Cach\'e, DB2} 
		\item[GPGPU:]{ \footnotesize CUDA, OpenCL} 
	\end{description} % End Skills list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}
		\item 
			\ressubheading{\href{http://www.epic.com}{Epic Systems}}{Verona,
			WI}{Software Developer}{Jan. 2011 -- Present} { \footnotesize
				\begin{itemize}
				  	\resitem{Lead pilot projects on revamping existing functionalities using
				  	next generation platform and technology;} 
				  	\resitem{Touch base with current and potential customers on a regular
				  	basis to analyze their requirements;} 
				  	\resitem{Design and implement both server and client features that
					have been committed to customers;}
					\resitem{Peer review other developers' work and provide constructive
					feedback to continuously improve the code quality;}
					\resitem{Participate in the whole cycle of testing and release, help draft 
					and review both test plans and release notes;}
					\resitem{Collect end users' feedback and prioritize bug fixes, collaborate
					with other roles to release updates promptly.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://synergy.cs.vt.edu}{SyNeRGY Lab}}{Blacksburg,
			VA}{Research Assistant}{Aug. 2009 -- Dec. 2010} { \footnotesize
				\begin{itemize}
					\resitem{Design and implement micro kernels to probe GPGPU performance 
					under varying frequencies;}
					\resitem{Publish research paper about green super computing using GPGPU
					in GreenCom 2010;} 
					\resitem{Admin infrastructure and computing resources for the reseach group.}   
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.green500.org}{The Green500 List}}{Blacksburg,
			VA}{Web Developer}{Aug. 2009 -- Dec. 2010} { \footnotesize
				\begin{itemize} 
					\resitem{Build the web submission system based on LAMP for The Green500
					List;} 
					\resitem{Design, implement, and optimize the backbone MySQL database of The
					Green500 List;}
					\resitem{Visualize large scale data using Google Visualization API and
					JavaScript Infovis Toolkit.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.isi.edu}{USC Information Sciences Institute}}{Arlington,
			VA}{Visiting Research Assistant}{May 2010 -- Aug. 2010} { \footnotesize
				\begin{itemize}
					\resitem{Parse several gigabytes of subversion and regression testing logs
					via Perl and Python to retrieve information;}
					\resitem{Store all parsed data in MySQL database and build internal web
					interface by PHP for easy access to the database;}
					\resitem{Visualize stored information via Java-based Processing framework, 
					generating treemaps and time series plots;}
					\resitem{Publish research paper in ESEM 2011.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://people.cs.vt.edu/~tilevich/}{Software
			Inovations Lab}}{Blacksburg, VA}{Research Assistant}{Aug. 2008 -- May 2009} 
			{\footnotesize
				\begin{itemize}
					\resitem{Design, implement, and test the remote conditionals of BRMI (Batch
					Remote Method Invocation);}
					\resitem{Design and implement the fundamental network communication
					infrastructure of RBI (Remote Batch Invocation);}
					\resitem{Both projects have achieved the goal of extending the
					functionality of existing Java RMI framework;}
					\resitem{Publish two research papers in top conferences, i.e., ICDCS 2009
					and ECOOP 2009 respectively.}
				\end{itemize}
				}
	\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.vt.edu}{Virginia Tech}}{Blacksburg,
			VA}{\href{http://www.cs.vt.edu/}{Master of Science
			in Computer Science}}{Aug. 2008 -- Dec. 2010}
		\item
			\ressubheading{\href{http://www.nju.edu.cn}{Nanjing University}}{Nanjing,
			China}{\href{http://cs.nju.edu.cn/}{Master of Engineering
			in Computer Science}}{Sep. 2006 -- Jun. 2008}
		\item
			\ressubheading{\href{http://www.nju.edu.cn}{Nanjing University}}{Nanjing,
			China}{\href{http://cs.nju.edu.cn/}{Bachelor of Science
			in Computer Science}}{Sep. 2002 -- Jun. 2006}
	\end{itemize} % End Education list

\end{document}
